Free surface computations in mantle convection models

### 2015-07-08 free-surface-paper.tex
Enhance caption

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/stability.pdf}
\label{fig:stability}
\caption{Left: stability region for the nonstandard finite difference scheme (green). For $\tau^*\le \tau_{\mathrm{max}}$ it is unconditionally stable.  Right: stability region for the quasi-implicit scheme (green).  For $\theta = 1$ it is unconditionally stable. In both cases the stability region for the forward Euler scheme is also shown in blue.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/stability.pdf}
\label{fig:stability}
\caption{Left: stability region for the nonstandard finite difference scheme (green). On the x-axis is the value of the stabilization time, in units of the minimum relaxation time $\tau_{\mathrm{min}}$.  On the y-axis is the value of the timestep, also in units of the minimum relaxation time. For $\tau^*\le \tau_{\mathrm{min}}$ it is unconditionally stable.  Right: stability region for the quasi-implicit scheme (green).  Again, the y axis is in units of the minumum relaxation time.  The x-axis shows the value of the stabilization parameter $\theta$. For $\theta = 1$ it is unconditionally stable. In both cases the stability region for the forward Euler scheme is also shown in blue.}
\end{figure}
